The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-05-01 doc/sec/papers/GRID09/paper.tex
little change again

\subsection{Performance comparison between HED and Axis2/C}
\label{sec:perhedandaxis}
Since the implementation of HED includes an alternative SOAP implementation
which is the base of the security related web services described in this paper, it is useful to
compare the performance of HED and other SOAP implementations. Here we compare 
the performance of HED and Axis2/C (v1.5.0), because we need to demostrate that the performance of HED
is at least comparable to other implementations. We do not compare the performance of HED 
with other SOAP implementations such as AxisJava, gSOAP, XSOAP4, etc., because a complete 
performance comparison between HED and all the other SOAP implementations is not the main 
goal of this paper to achieve, and a partial performance comparison is enough. Another reason
of choosing Axis2/C is because it is also implemented in C/C++ programming language.

@@

However, for some typical grid application scenarios, the client normally does
not need to continuously accomplish SAML2SSO profile. For instance, a user could submit a
job which needs a period of time (normally this period is much longer than a few
seconds) to execute, which launches an execution of SAML2SSO profile. 
This user could afterwards query the information as well as the result of
this job, which would launch another execution of SAML2SSO profile. On the other hand,
statistically, users will most probably not access grid system in a concurrent way, rather than in a random way.
Therefore, if we suppose that a user could access grid once per minute, in our test environment, we
can claim that for the case of disabled single sign-on, around 215 clients randomly can be 
supported with acceptable performance, while for the case of single sign-on enabled, around 340 
clients randomly can be supported with acceptable performance.

>>>>

\subsection{Performance comparison between HED and Axis2/C}
\label{sec:perhedandaxis}
Since the implementation of HED includes an alternative SOAP implementation
which is the base of the security related Grid/Web Services described in this paper, it is useful to
compare the performance of HED and other SOAP implementations. Here we compare 
the performance of HED and Axis2/C (v1.5.0), because we need to demostrate that the performance of HED
is at least comparable to other implementations. We do not compare the performance of HED 
with other SOAP implementations such as AxisJava, gSOAP, XSOAP4, etc., because a complete 
performance comparison between HED and all the other SOAP implementations is not the main 
goal of this paper to achieve, and a partial performance comparison is enough. Another reason
of choosing Axis2/C is because it is also implemented in C/C++ programming language.

@@

However, for some typical Grid application scenarios, the client normally does
not need to continuously accomplish SAML2SSO profile. For instance, a user could submit a
job which needs a period of time (normally this period is much longer than a few
seconds) to execute, which launches an execution of SAML2SSO profile. 
This user could afterwards query the information as well as the result of
this job, which would launch another execution of SAML2SSO profile. On the other hand,
statistically, users will most probably not access Grid system in a concurrent way, rather than in a random way.
Therefore, if we suppose that a user could access Grid once per minute, in our test environment, we
can claim that for the case of disabled single sign-on, around 215 clients randomly can be 
supported with acceptable performance, while for the case of single sign-on enabled, around 340 
clients randomly can be supported with acceptable performance.
